---
title: "Exercise 2"
author: "Micha Franz"
date: "2023-04-28"
output: 
  html_document:
    toc: yes
    toc_float: true
    code_folding: "show"
    css: style.css
---

**Packages**

```{r results=F, warning=F, message=F}
library(readr)
library(sf)
library(ggplot2)
library(dplyr)
library(mapview)
library(RColorBrewer)
```

***

## Task 1
```{r message=F}
wildschwein_BE <- read_delim("data/wildschwein_BE_2056.csv", ",") %>%
  st_as_sf(coords = c("E", "N"), crs = 2056, remove = FALSE)
```

***

## Task 2
```{r, warning=F}
wildschwein_BE <- wildschwein_BE %>%
  group_by(TierName) %>%
  mutate(diff_s = as.numeric(difftime(lead(DatetimeUTC), DatetimeUTC)))
```

*How many individuals were tracked?* **`r n_distinct(wildschwein_BE$TierID)`**\
*For how long were the individual tracked?* **See plot below**\
*Are there gaps?* **See plot below**\
*Were all individuals tracked concurrently or sequentially?* **See plot below**\

```{r class.source = 'fold-hide', out.width="100%"}
ggplot(wildschwein_BE, aes(DatetimeUTC, TierName)) +
  geom_point() +
  theme_minimal()
```

What is the temporal sampling interval between the locations?\
```{r class.source = 'fold-hide'}
print(summary(wildschwein_BE$diff_s))
```

***

## Task 3
```{r results=F}
wildschwein_BE <-  wildschwein_BE %>%
  mutate(steplength_m=sqrt((lead(E)-E)^2 + (lead(N)-N)^2)) %>%
  mutate(speed_ms=steplength_m/diff_s)
```

***

## Task 4
```{r class.source = 'fold-hide'}
caro_1 <- read_delim("data/caro60.csv", ",", show_col_types = F) %>%
  st_as_sf(coords = c("E", "N"), crs = 2056, remove = FALSE)
```

```{r}
caro_3 <- caro_1 %>%
  filter(row_number() %% 3 == 1) #filter using modulo

caro_6 <- caro_1 %>%
  filter(row_number() %% 6 == 1) #filter using modulo

caro_9 <- caro_1 %>%
  filter(row_number() %% 9 == 1) #filter using modulo
```  

```{r}
# calculating timelag, steplength and speed using a loop
for (interval in c("1", "3", "6", "9")){
  get_var_name <- paste0("caro_", interval)
  get_var <- eval(parse(text = get_var_name))

  caro_mutate <- get_var %>%
    mutate(diff_s = as.numeric(difftime(lead(DatetimeUTC), DatetimeUTC))) %>%
    mutate(steplength_m=sqrt((lead(E)-E)^2 + (lead(N)-N)^2)) %>%
    mutate(speed_ms=steplength_m/diff_s)
  assign(paste0("caro_", interval), caro_mutate)
}
```


```{r out.width="100%"}
# visualize trajectories different sampling intervals
# create a list of datasets to combine with caro_1
datasets <- list(caro_3, caro_6, caro_9)

# Loop over the datasets and generate a plot for each one
for (i in 1:length(datasets)) {
  
  plot <- ggplot() +
    geom_path(data = caro_1, aes(x = E, y = N, color = "1"), group = 1, alpha=1) +
    geom_point(data = caro_1, aes(x = E, y = N, color = "1"), size = 1.5) +
    geom_path(data = datasets[[i]], aes(x = E, y = N, color = as.character(i*3)), group = 1) +
    geom_point(data = datasets[[i]], aes(x = E, y = N, color = as.character(i*3)), size = 1.5) +
    scale_color_manual(values = c(alpha("#051F5E", 0.3), alpha("#f0bd00", 1)),
                     labels = c("1 minute", paste0(as.character(i*3)," minutes"))) +
    labs(color = "Sampling Interval") +
    theme_minimal() +
    ggtitle(paste("Comparing caro_1 with caro_", i*3, "-resampled data"))+
  theme(plot.title = element_text(hjust = 0.5))
  
  print(plot)
  cat("\n")
  cat("\n")
  cat("\n")
}
```

```{r out.width="100%"}
# visualize speed differences of different sampling intervals

ggplot() +
  geom_line(caro_1, mapping=aes(DatetimeUTC, speed_ms, color="1")) +
  geom_line(caro_3, mapping=aes(DatetimeUTC, speed_ms, color="2")) +
  geom_line(caro_6, mapping=aes(DatetimeUTC, speed_ms, color="3")) +
  geom_line(caro_9, mapping=aes(DatetimeUTC, speed_ms, color="4")) +
  scale_color_discrete(name = "Sampling Interval", labels = c("1 minute", "3 minutes", "6 minutes", "9 minutes")) + 
  labs(x="Time", y="Speed[m/s]") +
  ggtitle("Speed comparison of different sampling intervals") +
  theme(plot.title = element_text(hjust = 0.5))
```

***

## Task 5

***

## Task 6

Movement data added to repository.

***

## Task 7

```{r out.width="100%"}
posmo <- read_delim("data/posmo_mf.csv") %>%
  st_as_sf(coords=c("lon_x", "lat_y"), crs=4236) %>%
  mutate(day=as.character(as.Date(datetime))) # convert date to character, mapview's zcol doesn't recognize the date format somehow
pal <- c("#000000","#004949","#009292","#ff6db6","#ffb6db",
 "#490092","#006ddb","#b66dff","#6db6ff","#b6dbff",
 "#920000","#924900","#db6d00","#24ff24","#ffff6d")

mapview(posmo, zcol="day", col.regions=pal)
```


